Model LF

### 2022-12-16 paper version 2.Rmd
Commit

zz= ts(c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1), start = c(2005, 2), end =  c(2020,1), frequency = 4)

@@

shock= ts(c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0), start = c(2005, 2), end =  c(2020,1), frequency = 4)

@@

```{r}
#eq_h_nf = dummy_1*0.275*eq_h + dummy_2*eq_h_nf
#eq_h_f = dummy_1*0.663*eq_h + dummy_2*eq_h_f
#eq_h_row = dummy_1*0.062*eq_h  + dummy_2*eq_h_row 
```

@@

```{r}
#series  iba_h_tr = fn
```

@@

```{r}
## Creating the new shock variables
g_shock= g*1.02
prodk_ds_shock = prodk_ds
max_dp_shock= obs_dp_q
stat_reg_shock = ts(0.02, start = c(2005, 2), end =  c(2020,1), frequency = 4)

## Shock_1
pf_shock= pf+pf*0.1
pm_ds_shock= pm_ds+pm_ds*0.1

## Shock 2
iloan_shock= iloan + 0.03
idep_shock= idep + 0.03
ibd_shock= ibd + 0.03
iboa_shock= iboa + 0.03

## Shock 3

tax_rate1_shock= ts(c(0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369,0.369369), start = c(2005, 2), end =  c(2020,1), frequency = 4)

#### Shock variables 
shock_wage_ds_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_max_dp_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_g_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_reg_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_part_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_1_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_2_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_3_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_kuld_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_prod_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_lf_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

#### Sensitivity analysis variables 
sens1_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens1_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_low=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2_up=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens_3=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
disc=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
```

@@

COMMENT> 
IDENTITY> lf
EQ> lf = (part*pop)/1000
IF> shock_part_model <=0
IDENTITY> lf
EQ> lf = (part1*pop*(1-old_age_ratio))/1000
IF> shock_part_model > 0
IDENTITY> lf
EQ> lf = lf_test
IF> shock_lf_model > 0

@@

IDENTITY> part
EQ> part = part*1
IF> shock_part_model <= 0
IDENTITY> part
EQ> part = lf*1000/pop
IF> shock_part_model > 0
IDENTITY> part
EQ> part = lf*1000/pop
IF> shock_lf_model > 0

BEHAVIORAL> part1
TSRANGE 2006 2 2020 1
EQ> TSDELTALOG(part1) = beta_0 + beta_1*TSDELTALOG(TSLAG(part1,2)) + beta_2*TSDELTALOG(TSLAG(part1,3))  +beta_3*TSDELTALOG(TSLAG(kont_h_ratio,1)) +beta_4*TSDELTALOG(rw_ds)  +beta_5*TSDELTALOG(TSLAG(rw_ds,2)) +beta_6*TSDELTALOG(TSLAG(rw_ds,3))  + beta_8*LOG(TSLAG(part1,1))  + beta_9*log(TSLAG(rw_ds,1)) + beta_10*log(TSLAG(kont_h_ratio,1)) + beta_11*TSLAG(ur_ds,1)
COEFF> beta_0 beta_1 beta_2 beta_3 beta_4 beta_5 beta_6 beta_8 beta_9 beta_10 beta_11 
STORE> coe(16)

COMMENT> 
IDENTITY> kont_h_ratio
EQ> kont_h_ratio = kont_h / dp_person

COMMENT> Capital Stock with switches
IDENTITY> g
EQ> g = g*1
IF> shock_g_model <= 0
IDENTITY> g
EQ> g = g_shock
IF> shock_g_model > 0

@@

COMMENT> Lavet for at kunne støde til g 
IDENTITY> shock_part_model
EQ> shock_part_model = shock_part_model*1

@@

  b2_f_r = TIMESERIES(c(b2_f_r),   
                    START=c(2005,2),FREQ=4),
  b2_g_r = TIMESERIES(c(b2_g_r),   
                     START=c(2005,2),FREQ=4),
  p_tax = TIMESERIES(c(p_tax),   
                         START=c(2005,2),FREQ=4),
  p_tax_row = TIMESERIES(c(p_tax_row),   
                        START=c(2005,2),FREQ=4),
  p_sub = TIMESERIES(c(p_sub),   
                         START=c(2005,2),FREQ=4),
  p_sub_row = TIMESERIES(c(p_sub_row),   
                       START=c(2005,2),FREQ=4),
  zz = TIMESERIES(c(zz),   
                        START=c(2005,2),FREQ=4),
  i_equip_g_k = TIMESERIES(c(i_equip_g_k),   
                        START=c(2005,2),FREQ=4),
  i_equip_fc_k = TIMESERIES(c(i_equip_fc_k),   
                        START=c(2005,2),FREQ=4),
  i_bd_g_k = TIMESERIES(c(i_bd_g_k),   
                       START=c(2005,2),FREQ=4),
  i_bd_fc_k = TIMESERIES(c(i_bd_fc_k),   
                         START=c(2005,2),FREQ=4),
  i_adj_h_k = TIMESERIES(c(i_adj_h_k),   
                           START=c(2005,2),FREQ=4),
  i_adj_nfc_k = TIMESERIES(c(i_adj_nfc_k),   
                            START=c(2005,2),FREQ=4),

@@

e1= pr_c_unemp/2.5;e1
```

@@

e2= pr_c_unemp/2.5;e2
```

@@

e3= pr_c_unemp/2.5;e3
```

@@

**Macro effect with productivity**

```{r}
change_unemp_pr_05= (unemp_05 - unemp_bs56)/unemp_bs56
change_dp_person_pr_05= (dp_person_05 - dp_person_bs56)/dp_person_bs56
```

```{r}
e3= change_unemp_pr_05/change_dp_person_pr_05;e3
```

**Macro effect without productivity and wage**

```{r}
change_unemp_pr_07= (unemp_07 - unemp_bs7)/unemp_bs7
change_dp_person_pr_07= (dp_person_07 - dp_person_bs7)/dp_person_bs7
```

```{r}
e3= change_unemp_pr_07/change_dp_person_pr_07;e3
```

**Macro effect without productivity wages, and LF**

```{r}
change_unemp_pr_04= (unemp_04 - unemp_bs4)/unemp_bs4
change_dp_person_pr_04= (dp_person_04 - dp_person_bs4)/dp_person_bs4
```

```{r}
e3= change_unemp_pr_04/change_dp_person_pr_04;e3
```

**Macro effect without productivity**

```{r}
change_unemp_pr_07b= (unemp_07b - unemp_bs7b)/unemp_bs7b
change_dp_person_pr_07b= (dp_person_07b - dp_person_bs7b)/dp_person_bs7b
```

```{r}
e3= change_unemp_pr_07b/change_dp_person_pr_07b;e3
```

**Macro effect without productivity and lf**

```{r}
change_unemp_pr_08= (unemp_08 - unemp_bs8)/unemp_bs8
change_dp_person_pr_08= (dp_person_08 - dp_person_bs8)/dp_person_bs8
```

```{r}
e3= change_unemp_pr_08/change_dp_person_pr_08;e3
```

@@

### Micro elasticities
micro_elas_dp= 0.66
micro_elas_dørs= 0.51
micro_elas_fag= 0.36

### Macro elasticities
macro_elas_no_prod= 0.4
macro_elas_prod= 3
macro_elas_nowage= -0.04
macro_elas_short= 0.28
macro_elas_nowage_short= -0.05
### Unemployment rate

@@

marg_cost_c1= (micro_elas_fag)/(1-ur_fag); marg_cost_c1

@@

marg_cost_c2= (micro_elas_dp)/(1-ur_fag); marg_cost_c2

### Case 3

@@

marg_cost_c3= (micro_elas_dørs +macro_elas_no_prod )/(1-ur_fag); marg_cost_c3

### Case 3 no wage

@@

marg_cost_c3_w= (micro_elas_dørs +macro_elas_nowage )/(1-ur_fag); marg_cost_c3_w

## Komp_r er stadig den samme selv når jeg ikke har wage kanal med.

## Case 3 short version

@@

marg_cost_c3_w= (micro_elas_dørs +macro_elas_short )/(1-ur_fag); marg_cost_c3_w

# Sensitivitets analyse

## Sens1_low

### Baseline

Vi ændrer værdien i koefficienten i dp_person ligningen fra 0.95 til 0.85
```{r}
# Define add-factor list (defining shock)
constantAdjList_sens1_low <- list(

 sens1_low = TIMESERIES(sens1_low+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
sens_1_base_low <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_sens1_low
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_sb_low = sens_1_base_low$simulation$max_dp
wage_sb_low = sens_1_base_low$simulation$wage
komp_r_sb_low = sens_1_base_low$simulation$komp_r
part_sb_low = sens_1_base_low$simulation$part
yk_ds_sb_low = sens_1_base_low$simulation$yk_ds
pc_ds_sb_low = sens_1_base_low$simulation$pc_ds
unemp_sb_low = sens_1_base_low$simulation$unemp
dp_person_sb_low = sens_1_base_low$simulation$dp_person
nl_g_sb_low = sens_1_base_low$simulation$nl_g
```

### Scenario 1

Vi ændrer værdien i koefficienten i dp_person ligningen
```{r}
# Define add-factor list (defining shock)
constantAdjList1_sens1_low <- list(

 sens1_low = TIMESERIES(sens1_low+1 ,START=c(2006,3),  FREQ='Q'),
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q')
)

```{r}
# Simulate the model (following shock)
sens_1_S1_low <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1_sens1_low
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_s1_low = sens_1_S1_low$simulation$max_dp
wage_s1_low = sens_1_S1_low$simulation$wage
komp_r_s1_low = sens_1_S1_low$simulation$komp_r
part_s1_low = sens_1_S1_low$simulation$part
yk_ds_s1_low = sens_1_S1_low$simulation$yk_ds
pc_ds_s1_low = sens_1_S1_low$simulation$pc_ds
unemp_s1_low = sens_1_S1_low$simulation$unemp
dp_person_s1_low = sens_1_S1_low$simulation$dp_person
nl_g_s1_low = sens_1_S1_low$simulation$nl_g
```

## Sens1_up

### Baseline

Vi ændrer værdien i koefficienten i dp_person ligningen fra 0.95 til 0.85
```{r}
# Define add-factor list (defining shock)
constantAdjList_sens1_up <- list(

 sens1_up = TIMESERIES(sens1_up+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
sens_1_base_up <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_sens1_up
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_sb_up = sens_1_base_up$simulation$max_dp
wage_sb_up = sens_1_base_up$simulation$wage
komp_r_sb_up = sens_1_base_up$simulation$komp_r
part_sb_up = sens_1_base_up$simulation$part
yk_ds_sb_up = sens_1_base_up$simulation$yk_ds
pc_ds_sb_up = sens_1_base_up$simulation$pc_ds
unemp_sb_up = sens_1_base_up$simulation$unemp
dp_person_sb_up = sens_1_base_up$simulation$dp_person
nl_g_sb_up = sens_1_base_up$simulation$nl_g
```

### Scenario 1

Vi hæver estimated for max_dp på dp_person til 0.99. 
```{r}
# Define add-factor list (defining shock)
constantAdjList1_sens1_up <- list(

 sens1_up = TIMESERIES(sens1_up+1 ,START=c(2006,3),  FREQ='Q'),
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q')
)

```{r}
# Simulate the model (following shock)
sens_1_S1_up <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1_sens1_up
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_s1_up = sens_1_S1_up$simulation$max_dp
wage_s1_up = sens_1_S1_up$simulation$wage
komp_r_s1_up = sens_1_S1_up$simulation$komp_r
part_s1_up = sens_1_S1_up$simulation$part
yk_ds_s1_up = sens_1_S1_up$simulation$yk_ds
pc_ds_s1_up = sens_1_S1_up$simulation$pc_ds
unemp_s1_up = sens_1_S1_up$simulation$unemp
dp_person_s1_up = sens_1_S1_up$simulation$dp_person
nl_g_s1_up = sens_1_S1_up$simulation$nl_g
```

## Sens 1 plots

plot(((yk_ds_s1_up-yk_ds_sb_up)/yk_ds_sb_up)*100, col= "red", xlab= "Year", ylab= "% Change in GDP", main= "Sensitivity of GDP");
lines(((yk_ds_s1_low-yk_ds_sb_low) /yk_ds_sb_low)*100, col="black");
lines(((yk_ds_01 -yk_ds_00) /yk_ds_00)*100, col="blue");
legend("top", legend=c("Estimate 0.99",
                       "Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()

plot((unemp_s1_up-unemp_sb_up)*1000, col= "red", xlab= "Year", ylab= "Change in Unemployment (people)", main= "Sensitivity of Unemployment");
lines((unemp_s1_low-unemp_sb_low)*1000, col="black");
lines((unemp_01-unemp_00)*1000, col="blue");
legend("left", legend=c("Estimate 0.99",
                       "Estimate 0.85",
                       "Estimate 0.95"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

Effect on unemployment:

## Sens 2_ low

### Baseline

```{r}
# Define add-factor list (defining shock)
constantAdjList_sens2_low <- list(

 sens2_low = TIMESERIES(sens2_low+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
sens_2_bs_low <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_sens2_low
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_sbs2_low = sens_2_bs_low$simulation$max_dp
wage_sbs2_low = sens_2_bs_low$simulation$wage
komp_r_sbs2_low = sens_2_bs_low$simulation$komp_r
part_sbs2_low = sens_2_bs_low$simulation$part
yk_ds_sbs2_low = sens_2_bs_low$simulation$yk_ds
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
wage_ds_t_sbs2_low = sens_2_bs_low$simulation$wage_ds_t
pc_ds_sbs2_low = sens_2_bs_low$simulation$pc_ds
max_gap_sbs2_low = sens_2_bs_low$simulation$max_gap
wage_gap1_sbs2_low = sens_2_bs_low$simulation$wage_gap1
inflation_sbs2_low = sens_2_bs_low$simulation$inflation
wage_ds_sbs2_low = sens_2_bs_low$simulation$wage_ds
emp_sbs2_low = sens_2_bs_low$simulation$emp
nl_g_sbs2_low = sens_2_bs_low$simulation$nl_g
pconk_ds_sbs2_low = sens_2_bs_low$simulation$pconk_ds
unemp_sbs2_low = sens_2_bs_low$simulation$unemp
ik_sbs2_low = sens_2_bs_low$simulation$ik
xk_sbs2_low = sens_2_bs_low$simulation$xk
mk_sbs2_low = sens_2_bs_low$simulation$mk

net_export_sbs2_low= xk_sbs2_low - mk_sbs2_low

### Scenario 1

```{r}
# Define add-factor list (defining shock)
constantAdjList1_sens2_low <- list(

 sens2_low = TIMESERIES(sens2_low+1 ,START=c(2006,3),  FREQ='Q'),
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
sens_2_S1_low <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1_sens2_low
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_s2_low = sens_2_S1_low$simulation$max_dp
wage_s2_low = sens_2_S1_low$simulation$wage
komp_r_s2_low = sens_2_S1_low$simulation$komp_r
emp_s2_low = sens_2_S1_low$simulation$emp
yk_ds_s2_low = sens_2_S1_low$simulation$yk_ds
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
wage_ds_t_s2_low = sens_2_S1_low$simulation$wage_ds_t
pc_ds_s2_low = sens_2_S1_low$simulation$pc_ds
max_gap_s2_low = sens_2_S1_low$simulation$max_gap
wage_ds_s2_low = sens_2_S1_low$simulation$wage_ds
wage_gap1_s2_low = sens_2_S1_low$simulation$wage_gap1
wage_gap_s2_low = sens_2_S1_low$simulation$wage_gap
nl_g_s2_low = sens_2_S1_low$simulation$nl_g
inflation_s2_low = sens_2_S1_low$simulation$inflation
unemp_s2_low = sens_2_S1_low$simulation$unemp
ik_s2_low = sens_2_S1_low$simulation$ik
pconk_ds_s2_low = sens_2_S1_low$simulation$pconk_ds

xk_s2_low = sens_2_S1_low$simulation$xk
mk_s2_low = sens_2_S1_low$simulation$mk

net_export_s2_low= xk_s2_low - mk_s2_low
```

```{r}
plot((wage_ds_t_s2_low/wage_ds_t_sbs2_low), col= "red", ylim= c(1,1.04));
lines((wage_ds_t_02/wage_ds_t_bs2), col="black");
legend("top", legend=c("wage_gap limit 40%",
                       "Wage_gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((inflation_s2_low-inflation_sbs2_low), col= "red", ylim= c(-0.0004, 0.0035));
lines((inflation_02-inflation_bs2), col="black");
legend("top", legend=c("wage_gap limit 40%",
                       "Wage_gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot((wage_ds_s2_low/wage_ds_sbs2_low), col= "red", ylim= c(0.995, 1.02));
lines((wage_ds_02/wage_ds_bs2), col="black");
legend("top", legend=c("wage_gap limit 40%",
                       "Wage_gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

Effect on unemployment:

```{r}
plot((unemp_s2_low-unemp_sbs2_low)*1000, col= "red")
```

## Sens 2_up

We change the wage gap allowed to be 44%.

### Baseline

```{r}
# Define add-factor list (defining shock)
constantAdjList_sens2_up <- list(

 sens2_up = TIMESERIES(sens2_up+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
sens_2_bs_up <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_sens2_up
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_sbs2_up = sens_2_bs_up$simulation$max_dp
wage_sbs2_up = sens_2_bs_up$simulation$wage
komp_r_sbs2_up = sens_2_bs_up$simulation$komp_r
part_sbs2_up = sens_2_bs_up$simulation$part
yk_ds_sbs2_up = sens_2_bs_up$simulation$yk_ds
pc_ds_sbs2_up = sens_2_bs_up$simulation$pc_ds
wage_ds_t_sbs2_up = sens_2_bs_up$simulation$wage_ds_t
pc_ds_sbs2_up = sens_2_bs_up$simulation$pc_ds
max_gap_sbs2_up = sens_2_bs_up$simulation$max_gap
wage_gap1_sbs2_up = sens_2_bs_up$simulation$wage_gap1
inflation_sbs2_up = sens_2_bs_up$simulation$inflation
wage_ds_sbs2_up = sens_2_bs_up$simulation$wage_ds
unemp_sbs2_up = sens_2_bs_up$simulation$unemp
u_ds_sbs2_up = sens_2_bs_up$simulation$u_ds
nl_g_sbs2_up = sens_2_bs_up$simulation$nl_g
ik_sbs2_up = sens_2_bs_up$simulation$ik
pconk_ds_sbs2_up = sens_2_bs_up$simulation$pconk_ds

xk_ds_sbs2_up = sens_2_bs_up$simulation$xk_ds
mk_ds_sbs2_up = sens_2_bs_up$simulation$mk_ds
net_balance_sbs2_up= xk_ds_sbs2_up - mk_ds_sbs2_up
```

### Scenario 1

We look at a change in the wage-gap from 0.4 to 0.45 that the unions will demand at a wage negotiation.

```{r}
# Define add-factor list (defining shock)
constantAdjList1_sens2_up <- list(

 sens2_up = TIMESERIES(sens2_up+1 ,START=c(2006,3),  FREQ='Q'),
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
sens_2_S1_up <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1_sens2_up
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_s2_up = sens_2_S1_up$simulation$max_dp
wage_s2_up = sens_2_S1_up$simulation$wage
komp_r_s2_up = sens_2_S1_up$simulation$komp_r
unemp_s2_up = sens_2_S1_up$simulation$unemp
yk_ds_s2_up = sens_2_S1_up$simulation$yk_ds
pc_ds_s2_up = sens_2_S1_up$simulation$pc_ds
wage_ds_t_s2_up = sens_2_S1_up$simulation$wage_ds_t
pc_ds_s2_up = sens_2_S1_up$simulation$pc_ds
max_gap_s2_up = sens_2_S1_up$simulation$max_gap
wage_ds_s2_up = sens_2_S1_up$simulation$wage_ds
wage_gap1_s2_up = sens_2_S1_up$simulation$wage_gap1
wage_gap_s2_up = sens_2_S1_up$simulation$wage_gap
u_ds_s2_up = sens_2_S1_up$simulation$u_ds
inflation_s2_up = sens_2_S1_up$simulation$inflation
nl_g_s2_up = sens_2_S1_up$simulation$nl_g

ik_s2_up = sens_2_S1_up$simulation$ik
pconk_ds_s2_up = sens_2_S1_up$simulation$pconk_ds

xk_ds_s2_up = sens_2_S1_up$simulation$xk_ds
mk_ds_s2_up = sens_2_S1_up$simulation$mk_ds
net_balance_s2_up= xk_ds_s2_up - mk_ds_s2_up

## Sens 2 plots

par(mfrow=c(2,2))

plot(((wage_ds_t_s2_up-wage_ds_t_sbs2_up)/wage_ds_t_sbs2_up)*100, col= "red", ylab= "% change in Target Wage" ,  main= "Targeted Wage");
lines(((wage_ds_t_s2_low- wage_ds_t_sbs2_low)/wage_ds_t_sbs2_low)*100, col="black");
lines(((wage_ds_t_02-wage_ds_t_bs2)/wage_ds_t_bs2)*100, col="blue");
legend("top", legend=c("Wage-gap limit 44%",
                       "Wage-gap limit 40%",
                       "Wage-gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()

plot(((wage_ds_s2_up-wage_ds_sbs2_up)/wage_ds_sbs2_up)*100, col= "red", ylab="% change in Wages", main= "Wage");
lines(((wage_ds_s2_low-wage_ds_sbs2_low)/wage_ds_sbs2_low)*100, col="black");
lines(((wage_ds_02-wage_ds_bs2)/wage_ds_bs2)*100, col="blue");
legend("top", legend=c("Wage-gap limit 44%",
                       "Wage-gap limit 40%",
                       "Wage-gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()

plot((unemp_s2_up - unemp_sbs2_up)*1000, col= "red", ylab= "Change in Unemployment (people)", main= "Sensitivity of Unemployment");
lines((unemp_s2_low - unemp_sbs2_low)*1000, col="black");
lines((unemp_02 - unemp_bs2)*1000, col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()

plot(((yk_ds_s2_up-yk_ds_sbs2_up) / yk_ds_sbs2_up)*100, col= "red", ylab= "% Change inm GDP", main= "Sensitivity of GDP");
lines(((yk_ds_s2_low -yk_ds_sbs2_low)/ yk_ds_sbs2_low)*100, col="black");
lines(((yk_ds_02 -yk_ds_bs2)/ yk_ds_bs2)*100, col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

```{r}
plot(((wage_ds_s2_up-wage_ds_sbs2_up)/wage_ds_sbs2_up)*100, col= "red", ylab="% change in Wages", main= "Wage");
lines(((wage_ds_s2_low-wage_ds_sbs2_low)/wage_ds_sbs2_low)*100, col="black");
lines(((wage_ds_02-wage_ds_bs2)/wage_ds_bs2)*100, col="blue");
legend("top", legend=c("Wage-gap limit 44%",
                       "Wage-gap limit 40%",
                       "Wage-gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

```{r}
plot((ik_s2_up - ik_sbs2_up), col= "red", main= "Change in Investments");
lines((ik_s2_low - ik_sbs2_low), col="black");
lines((ik_02 - ik_bs2), col="blue");
legend("left", legend=c("Wage Gap limit 44%",
                        "Wage gap limit 40%",
                       "Wage gap limit 42%"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black", "blue"));
grid()
```

>>>>

@@

@@

@@

@@

```{r}
## Creating the new shock variables
max_dp_shock= obs_dp_q
stat_reg_shock = ts(0.02, start = c(2005, 2), end =  c(2020,1), frequency = 4)

#### Shock variables 
shock_wage_ds_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_max_dp_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_reg_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_kuld_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_prod_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
shock_lf_model=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

#### Sensitivity analysis variables

@@

COMMENT> 
IDENTITY> lf
EQ> lf = (part*pop)/1000
IF> shock_lf_model <=0
IDENTITY> lf
EQ> lf = lf_test
IF> shock_lf_model > 0

@@

@@

@@

  b2_f_r = TIMESERIES(c(b2_f_r),   
                    START=c(2005,2),FREQ=4),
  b2_g_r = TIMESERIES(c(b2_g_r),   
                     START=c(2005,2),FREQ=4),
  p_tax = TIMESERIES(c(p_tax),   
                         START=c(2005,2),FREQ=4),
  p_tax_row = TIMESERIES(c(p_tax_row),   
                        START=c(2005,2),FREQ=4),
  p_sub = TIMESERIES(c(p_sub),   
                         START=c(2005,2),FREQ=4),
  p_sub_row = TIMESERIES(c(p_sub_row),   
                       START=c(2005,2),FREQ=4),
  i_equip_g_k = TIMESERIES(c(i_equip_g_k),   
                        START=c(2005,2),FREQ=4),
  i_equip_fc_k = TIMESERIES(c(i_equip_fc_k),   
                        START=c(2005,2),FREQ=4),
  i_bd_g_k = TIMESERIES(c(i_bd_g_k),   
                       START=c(2005,2),FREQ=4),
  i_bd_fc_k = TIMESERIES(c(i_bd_fc_k),   
                         START=c(2005,2),FREQ=4),
  i_adj_h_k = TIMESERIES(c(i_adj_h_k),   
                           START=c(2005,2),FREQ=4),
  i_adj_nfc_k = TIMESERIES(c(i_adj_nfc_k),   
                            START=c(2005,2),FREQ=4),

@@

e1_micro= pr_c_unemp/2.5;e1_micro
```

@@

e2_micro= pr_c_unemp/2.5;e2_micro
```

@@

e3_micro= pr_c_unemp/2.5;e3_micro
```

@@

**Macro effect with ALL**

```{r}
change_unemp_pr_01= (unemp_01 - unemp_bs1)/unemp_bs1
change_dp_person_pr_01= (dp_person_01 - dp_person_bs1)/dp_person_bs1
```

```{r}
e1_macro= change_unemp_pr_01/change_dp_person_pr_01;e1_macro
```

**Macro effect without LF**

```{r}
change_unemp_pr_02= (unemp_02 - unemp_bs2)/unemp_bs2
change_dp_person_pr_02= (dp_person_02 - dp_person_bs2)/dp_person_bs2
```

```{r}
e2_macro= change_unemp_pr_02/change_dp_person_pr_02;e2_macro
```

**Macro effect without wages, and LF**

```{r}
change_unemp_pr_03= (unemp_03 - unemp_bs3)/unemp_bs3
change_dp_person_pr_03= (dp_person_03 - dp_person_bs3)/dp_person_bs3
```

```{r}
e3_macro= change_unemp_pr_03/change_dp_person_pr_03;e3_macro
```

@@

#### Micro elasticity

e1_micro ## IS-Commission
e2_micro ## DØRS
e3_micro ## Fagforeninger

#### Macro elasticity

mean_e1_macro= mean(window(e1_macro, start= c(2019,2))) # All channels
mean_e2_macro= mean(window(e2_macro, start= c(2019,2))) #Except LF channel 
mean_e3_macro= mean(window(e3_macro, start= c(2019,2))) #Except LF and Wage-channel

### Unemployment rate

@@

marg_cost_c1= (e3_micro)/(1-ur_fag); marg_cost_c1

@@

marg_cost_c2= (e1_micro)/(1-ur_fag); marg_cost_c2

### Case 3 All

@@

marg_cost_c3= (e2_micro +mean_e1_macro)/(1-ur_fag); marg_cost_c3

### Case 3 Exept LF

@@

marg_cost_c3_w= (e2_micro +mean_e2_macro )/(1-ur_fag); marg_cost_c3_w

### Case 3 Exept LF and Wage

@@

marg_cost_c3_w= (e2_micro +mean_e3_macro )/(1-ur_fag); marg_cost_c3_w
